---
  title: "Analytics Cup"
output:
  html_document:
  df_print: paged
html_notebook: default
pdf_document: default
---
  
  # 1) Libraries & Data Import
  
  First, we import necessary libraries and set global options.

```{r}
library(tidyverse)
library(lubridate) # data exploration
library(summarytools) # for user-friendly html summaries of data
library(ggmap) # for plotting data on a map
library(tidymodels) # for meta-ml
library(corrplot)
library(party)
library(randomForest)
# let's set some global options
options(dplyr.width = Inf) # show all columns when printing to console
theme_set(theme_minimal()) # select a lightweight ggplot theme for cleaner plotting
set.seed(2022)
```

Next, we import our csv datasets to dataframes

```{r}
customers <- read_csv(
  'Training_Data_AC2022/customers.csv'
)
customers
transactions <- read_csv(
  'Training_Data_AC2022/transactions.csv'
)
transactions
geo <- read_csv(
  'Training_Data_AC2022/geo.csv'
)
geo
```



# 2) Pre-processing Data

## 2.1) Merging all dataframes into one

```{r}
## Fix country string
customers$COUNTRY <- gsub('Switzerland', 'CH', customers$COUNTRY)
customers$COUNTRY <- gsub('France', 'FR', customers$COUNTRY)
## Fix customer string
transactions <- transactions %>% mutate(CUSTOMER = str_replace_all(transactions$CUSTOMER, '"', ''))
transactions <- transactions %>% mutate(CUSTOMER = str_replace_all(transactions$CUSTOMER, "\\\\", ''))
transactions <- transactions %>% 
  mutate(
    CUSTOMER = as.double(CUSTOMER)
  )
## Create unqie CUSTOMER_ID in the customers dataframe
customers$CUSTOMER_ID <- paste(customers$CUSTOMER,customers$COUNTRY,sep="")
## Merge transactions and geo dataframes based on the SALES_LOCATION column
df <- merge(x = transactions, y = geo, by = "SALES_LOCATION", all.x = TRUE)
## Create CUSTOMER_ID in the merged dataframe
df$CUSTOMER_ID <- paste(df$CUSTOMER,df$COUNTRY,sep="")
## Merge dataframe df and customers on CUSTOMER_ID
df <- merge(x = df, y = customers, by = "CUSTOMER_ID", all.x = TRUE)
```

## 2.2) Data cleaning

Handle offers with one MO_ID only
```{r}
df$MULTIPLE_OFFER <- if_else(!duplicated(df$MO_ID), 0, 1)
df <- df %>% select(-END_CUSTOMER, -END_CUSTOMER, -SALES_OFFICE, -SO_ID, )
df <- df %>% select(-CUSTOMER.x, -CUSTOMER.y, -COUNTRY.y, )
```

Fix target variable OFFER_STATUS
```{r}
df <- df %>% mutate(
  OFFER_STATUS=toupper(OFFER_STATUS)
)
df$OFFER_STATUS[df$OFFER_STATUS == "LOSE"] <- "LOST"
df$OFFER_STATUS[df$OFFER_STATUS == "WIN"] <- "WON"
```

Remove Tech EPS
```{r}
df <- df[df$TECH !='EPS', ]  
```

Create factors
```{r}
df <- df %>% mutate(
  SALES_LOCATION = factor(SALES_LOCATION, labels = as.vector(unique(df$SALES_LOCATION))[!is.na(as.vector(unique(df$SALES_LOCATION)))]),
  PRICE_LIST = factor(PRICE_LIST, labels = as.vector(unique(df$PRICE_LIST))),
  BUSINESS_TYPE = factor(BUSINESS_TYPE, labels = as.vector(unique(df$BUSINESS_TYPE))),
  OFFER_STATUS = factor(OFFER_STATUS, labels = as.vector(unique(df$OFFER_STATUS))[!is.na(as.vector(unique(df$OFFER_STATUS)))]),
  SALES_BRANCH = factor(SALES_BRANCH, labels = as.vector(unique(df$SALES_BRANCH))[!is.na(as.vector(unique(df$SALES_BRANCH)))]),
  TECH = factor(TECH, labels = as.vector(unique(df$TECH))[!is.na(as.vector(unique(df$TECH)))]),
  OFFER_TYPE = factor(OFFER_TYPE, labels = as.vector(unique(df$OFFER_TYPE))[!is.na(as.vector(unique(df$OFFER_TYPE)))]),
  OWNERSHIP = factor(OWNERSHIP, labels = as.vector(unique(df$OWNERSHIP))[!is.na(as.vector(unique(df$OWNERSHIP)))]),
  CURRENCY = factor(CURRENCY, labels = as.vector(unique(df$CURRENCY))[!is.na(as.vector(unique(df$CURRENCY)))]),
)
```

Handle dates
```{r}
df <- df %>% mutate(REV_CURRENT_YEAR = str_replace_all(df$REV_CURRENT_YEAR, '"', ''))
df <- df %>% mutate(REV_CURRENT_YEAR = str_replace_all(df$REV_CURRENT_YEAR, "\\\\", ''))
df$REV_CURRENT_YEAR <- as.integer(df$REV_CURRENT_YEAR)
df <- df %>% mutate(CREATION_YEAR = str_replace_all(df$CREATION_YEAR, "/", '.'))
df$CREATION_YEAR <- as.Date(df$CREATION_YEAR, format="%d.%m.%Y")
df %>% mutate(CREATION_YEAR = str_replace_all(df$CREATION_YEAR, "/", '.'))
#remove Seconds
for (i in 1:length(df$SO_CREATED_DATE)) {
  if (nchar(df$SO_CREATED_DATE[i], type = "chars") > 16) {
    df$SO_CREATED_DATE[i] <- substring(df$SO_CREATED_DATE[i],1,nchar(df$SO_CREATED_DATE[i])-3)
  }}
for (i in 1:length(df$MO_CREATED_DATE)) {
  if (nchar(df$MO_CREATED_DATE[i], type = "chars") > 16) {
    df$MO_CREATED_DATE[i] <- substring(df$MO_CREATED_DATE[i],1,nchar(df$MO_CREATED_DATE[i])-3)
  }}
#als Datum
df$SO_CREATED_TIME <- as_datetime(df$SO_CREATED_DATE, format = '%d.%m.%Y %H:%M') 
for (i in 1:length(df$SO_CREATED_TIME)) {
  if(is.na(df$SO_CREATED_TIME[i])) {
    df$SO_CREATED_TIME[i] <- as_datetime(df$SO_CREATED_DATE[i], format = '%Y-%m-%d %H:%M') 
  }}
df$SO_CREATED_DATE <- df$SO_CREATED_TIME
df$SO_CREATED_TIME <- NULL 
df$MO_CREATED_TIME <- as_datetime(df$MO_CREATED_DATE, format = '%d.%m.%Y %H:%M') 
for (i in 1:length(df$MO_CREATED_TIME)) {
  if(is.na(df$MO_CREATED_TIME[i])) {
    df$MO_CREATED_TIME[i] <- as_datetime(df$MO_CREATED_DATE[i], format = '%Y-%m-%d %H:%M') 
  }}
df$MO_CREATED_DATE <- df$MO_CREATED_TIME
df$MO_CREATED_TIME <- NULL
df$MO_Weekday <- format(df$MO_CREATED_DATE, format="%a")
df$SO_Weekday <- format(df$SO_CREATED_DATE, format="%a")
df$SO_day <- format(df$SO_CREATED_DATE, format = "%d")
df$MO_day <- format(df$MO_CREATED_DATE, format = "%d")
df$SO_month <- format(df$SO_CREATED_DATE, format = "%m")
df$MO_month <- format(df$MO_CREATED_DATE, format = "%m")
df$SO_year <- format(df$SO_CREATED_DATE, format = "%Y")
df$MO_year <- format(df$MO_CREATED_DATE, format = "%Y")
#SO_Time <- hour(df$SO_CREATED_DATE)*60 + minute(df$SO_CREATED_DATE)
#MO_Time <- hour(df$MO_CREATED_DATE)*60 + minute(df$MO_CREATED_DATE)
df$MO_hours <- format(df$MO_CREATED_DATE, format = "%H")
df$SO_hours <- format(df$SO_CREATED_DATE, format = "%H")
df <- df %>% mutate(
  #SO_Time = factor(SO_Time, labels = as.vector(unique(df$SO_Time))[!is.na(as.vector(unique(df$SO_Time)))]),
  #MO_Time = factor(MO_Time, labels = as.vector(unique(df$MO_Time))[!is.na(as.vector(unique(df$MO_Time)))]),
  MO_Weekday = factor(MO_Weekday, labels = as.vector(unique(df$MO_Weekday))[!is.na(as.vector(unique(df$MO_Weekday)))]),
  SO_Weekday = factor(SO_Weekday, labels = as.vector(unique(df$SO_Weekday))[!is.na(as.vector(unique(df$SO_Weekday)))]),
)
```

## 2.3) Create data split

Predict OFFER_STATUS of the submission data

```{r}
submission <- df[!is.na(df$TEST_SET_ID), ]
df <- df %>% drop_na(REV_CURRENT_YEAR.1)
df <- df %>% drop_na(SALES_LOCATION)
df <- df %>% drop_na(ISIC)

# 4) Training

library(h2o)

h2o.init()
independent <- c(names(train))
independent <- independent[! independent %in% c("OFFER_STATUS")]

train <- df[is.na(df$TEST_SET_ID), ]
train <- train %>% select(-TEST_SET_ID, )

train$SO_day <- as.factor(train$SO_day)
train$CUSTOMER_ID <- as.factor(train$CUSTOMER_ID)
train$MO_hours <- as.factor(train$MO_hours)
train$SO_month <- as.factor(train$SO_month)
train$MO_day <- as.factor(train$MO_day)
train$MO_month <- as.factor(train$MO_month)
train$COUNTRY.x <- as.factor(train$COUNTRY.x)
train$SO_year <- as.factor(train$SO_year)
train$MO_ID <- as.factor(train$MO_ID)
train$MO_year <- as.factor(train$MO_year)
train$SO_hours <- as.factor(train$SO_hours)

h2o_split <-  as.h2o(train)
#h2o_splited <- h2o.splitFrame(h2o_split, ratios = 0.125, seed = 2022)
#h2o_train <- h2o_splited[[2]]
#h2o_test <- h2o_splited[[1]]

#h2o_auto = h2o.automl(y = "OFFER_STATUS", x = independent ,training_frame  = h2o_train, validation_frame = h2o_test, max_runtime_secs = 300, seed = 2022) #currently set to ~4h
h2o_auto = h2o.automl(y = "OFFER_STATUS",training_frame  = h2o_split, max_runtime_secs = 30, seed = 2022, balance_classes = TRUE, stopping_metric = "misclassification" ) #currently set to ~4h

h2o_auto
h2o_auto@leader

h2o_submission <-  as.h2o(submission)
h2o_submission_preditions <- h2o.predict(h2o_auto, newdata = h2o_submission)

model <- h2o.getModel(model_id = h2o_auto@leader@model_id)

submission_preditions <- as.data.frame(h2o_submission_preditions)
```

## 4.4) Create submission

Create submission file

```{r}
submission_final <- submission
submission_final$OFFER_STATUS <- submission_preditions$predict
print(nrow(submission_final[submission_final$OFFER_STATUS == "LOST",]))
print(nrow(submission_final[submission_final$OFFER_STATUS == "WON",]))


submission_file_df <- submission_final %>% select(TEST_SET_ID, OFFER_STATUS)
submission_file_df$OFFER_STATUS <- ifelse(submission_file_df$OFFER_STATUS == 'WON', 1, 0)
summary(submission_file_df)

write.csv(submission_file_df, 'predictions_fierce_pigeon_SUBMISSION_NUMBER.csv', row.names = FALSE)
```

```{r}
knitr::purl("index.Rmd")
```
