---
title: "Analytics Cup"
output:
  html_document:
    df_print: paged
  html_notebook: default
  pdf_document: default
---

# 1) Libraries & Data Import

First, we import necessary libraries and set global options.

```{r}
library(tidyverse)
library(lubridate) # data exploration
library(summarytools) # for user-friendly html summaries of data
library(ggmap) # for plotting data on a map
library(tidymodels) # for meta-ml
library(corrplot)
library(party)
library(randomForest)

# let's set some global options
options(dplyr.width = Inf) # show all columns when printing to console
theme_set(theme_minimal()) # select a lightweight ggplot theme for cleaner plotting
set.seed(2022)
```

Next, we import our csv datasets to dataframes

```{r}
customers <- read_csv(
  'Training_Data_AC2022/customers.csv'
)
customers

transactions <- read_csv(
  'Training_Data_AC2022/transactions.csv'
)
transactions

geo <- read_csv(
  'Training_Data_AC2022/geo.csv'
)
geo
```



# 2) Pre-processing Data

## 2.1) Merging all dataframes into one

```{r}
## Fix country string
customers$COUNTRY <- gsub('Switzerland', 'CH', customers$COUNTRY)
customers$COUNTRY <- gsub('France', 'FR', customers$COUNTRY)

## Fix customer string
transactions <- transactions %>% mutate(CUSTOMER = str_replace_all(transactions$CUSTOMER, '"', ''))
transactions <- transactions %>% mutate(CUSTOMER = str_replace_all(transactions$CUSTOMER, "\\\\", ''))

transactions <- transactions %>% 
  mutate(
    CUSTOMER = as.double(CUSTOMER)
  )

## Create unqie CUSTOMER_ID in the customers dataframe
customers$CUSTOMER_ID <- paste(customers$CUSTOMER,customers$COUNTRY,sep="")

## Merge transactions and geo dataframes based on the SALES_LOCATION column
df <- merge(x = transactions, y = geo, by = "SALES_LOCATION", all.x = TRUE)

## Create CUSTOMER_ID in the merged dataframe
df$CUSTOMER_ID <- paste(df$CUSTOMER,df$COUNTRY,sep="")

## Merge dataframe df and customers on CUSTOMER_ID
df <- merge(x = df, y = customers, by = "CUSTOMER_ID", all.x = TRUE)
```

## 2.2) Data cleaning

Handle offers with one MO_ID only
```{r}
df$MULTIPLE_OFFER <- if_else(!duplicated(df$MO_ID), 0, 1)

df <- df %>% select(-END_CUSTOMER, -END_CUSTOMER, -SALES_OFFICE, -SO_ID, )
df <- df %>% select(-CUSTOMER.x, -CUSTOMER.y, -COUNTRY.y, )
```

Fix target variable OFFER_STATUS
```{r}
df <- df %>% mutate(
  OFFER_STATUS=toupper(OFFER_STATUS)
)
df$OFFER_STATUS[df$OFFER_STATUS == "LOSE"] <- "LOST"
df$OFFER_STATUS[df$OFFER_STATUS == "WIN"] <- "WON"
```

Remove Tech EPS
```{r}
df <- df[df$TECH !='EPS', ]  
```

Create factors
```{r}
df <- df %>% mutate(
  SALES_LOCATION = factor(SALES_LOCATION, labels = as.vector(unique(df$SALES_LOCATION))[!is.na(as.vector(unique(df$SALES_LOCATION)))]),
  PRICE_LIST = factor(PRICE_LIST, labels = as.vector(unique(df$PRICE_LIST))),
  BUSINESS_TYPE = factor(BUSINESS_TYPE, labels = as.vector(unique(df$BUSINESS_TYPE))),
  OFFER_STATUS = factor(OFFER_STATUS, labels = as.vector(unique(df$OFFER_STATUS))[!is.na(as.vector(unique(df$OFFER_STATUS)))]),
  SALES_BRANCH = factor(SALES_BRANCH, labels = as.vector(unique(df$SALES_BRANCH))[!is.na(as.vector(unique(df$SALES_BRANCH)))]),
  TECH = factor(TECH, labels = as.vector(unique(df$TECH))[!is.na(as.vector(unique(df$TECH)))]),
  OFFER_TYPE = factor(OFFER_TYPE, labels = as.vector(unique(df$OFFER_TYPE))[!is.na(as.vector(unique(df$OFFER_TYPE)))]),
  OWNERSHIP = factor(OWNERSHIP, labels = as.vector(unique(df$OWNERSHIP))[!is.na(as.vector(unique(df$OWNERSHIP)))]),
  CURRENCY = factor(CURRENCY, labels = as.vector(unique(df$CURRENCY))[!is.na(as.vector(unique(df$CURRENCY)))]),
)
```

Handle dates
```{r}
df <- df %>% mutate(REV_CURRENT_YEAR = str_replace_all(df$REV_CURRENT_YEAR, '"', ''))
df <- df %>% mutate(REV_CURRENT_YEAR = str_replace_all(df$REV_CURRENT_YEAR, "\\\\", ''))
df$REV_CURRENT_YEAR <- as.integer(df$REV_CURRENT_YEAR)

df <- df %>% mutate(CREATION_YEAR = str_replace_all(df$CREATION_YEAR, "/", '.'))
df$CREATION_YEAR <- as.Date(df$CREATION_YEAR, format="%d.%m.%Y")

df %>% mutate(CREATION_YEAR = str_replace_all(df$CREATION_YEAR, "/", '.'))

#remove Seconds
for (i in 1:length(df$SO_CREATED_DATE)) {
  if (nchar(df$SO_CREATED_DATE[i], type = "chars") > 16) {
    df$SO_CREATED_DATE[i] <- substring(df$SO_CREATED_DATE[i],1,nchar(df$SO_CREATED_DATE[i])-3)
  }}
for (i in 1:length(df$MO_CREATED_DATE)) {
  if (nchar(df$MO_CREATED_DATE[i], type = "chars") > 16) {
    df$MO_CREATED_DATE[i] <- substring(df$MO_CREATED_DATE[i],1,nchar(df$MO_CREATED_DATE[i])-3)
  }}

#als Datum
df$SO_CREATED_TIME <- as_datetime(df$SO_CREATED_DATE, format = '%d.%m.%Y %H:%M') 
for (i in 1:length(df$SO_CREATED_TIME)) {
  if(is.na(df$SO_CREATED_TIME[i])) {
    df$SO_CREATED_TIME[i] <- as_datetime(df$SO_CREATED_DATE[i], format = '%Y-%m-%d %H:%M') 
  }}
df$SO_CREATED_DATE <- df$SO_CREATED_TIME
df$SO_CREATED_TIME <- NULL 

df$MO_CREATED_TIME <- as_datetime(df$MO_CREATED_DATE, format = '%d.%m.%Y %H:%M') 
for (i in 1:length(df$MO_CREATED_TIME)) {
  if(is.na(df$MO_CREATED_TIME[i])) {
    df$MO_CREATED_TIME[i] <- as_datetime(df$MO_CREATED_DATE[i], format = '%Y-%m-%d %H:%M') 
  }}
df$MO_CREATED_DATE <- df$MO_CREATED_TIME
df$MO_CREATED_TIME <- NULL

df$MO_Weekday <- format(df$MO_CREATED_DATE, format="%a")
df$SO_Weekday <- format(df$SO_CREATED_DATE, format="%a")

df$SO_day <- format(df$SO_CREATED_DATE, format = "%d")
df$MO_day <- format(df$MO_CREATED_DATE, format = "%d")

df$SO_month <- format(df$SO_CREATED_DATE, format = "%m")
df$MO_month <- format(df$MO_CREATED_DATE, format = "%m")

df$SO_year <- format(df$SO_CREATED_DATE, format = "%Y")
df$MO_year <- format(df$MO_CREATED_DATE, format = "%Y")

#SO_Time <- hour(df$SO_CREATED_DATE)*60 + minute(df$SO_CREATED_DATE)
#MO_Time <- hour(df$MO_CREATED_DATE)*60 + minute(df$MO_CREATED_DATE)

df$MO_hours <- format(df$MO_CREATED_DATE, format = "%H")
df$SO_hours <- format(df$SO_CREATED_DATE, format = "%H")

df <- df %>% mutate(
  #SO_Time = factor(SO_Time, labels = as.vector(unique(df$SO_Time))[!is.na(as.vector(unique(df$SO_Time)))]),
  #MO_Time = factor(MO_Time, labels = as.vector(unique(df$MO_Time))[!is.na(as.vector(unique(df$MO_Time)))]),
  MO_Weekday = factor(MO_Weekday, labels = as.vector(unique(df$MO_Weekday))[!is.na(as.vector(unique(df$MO_Weekday)))]),
  SO_Weekday = factor(SO_Weekday, labels = as.vector(unique(df$SO_Weekday))[!is.na(as.vector(unique(df$SO_Weekday)))]),
)
```

## 2.3) Create data split

```{r}
submission <- df[!is.na(df$TEST_SET_ID), ]

df <- df %>% drop_na(REV_CURRENT_YEAR.1)
df <- df %>% drop_na(SALES_LOCATION)
df <- df %>% drop_na(ISIC)

train <- df[is.na(df$TEST_SET_ID), ]

train <- train %>% select(-TEST_SET_ID, )
train
```

```{r}
submission
```
# 3) Exploratory Analysis

## 3.1) Some visualisations

```{r}
## Offer status compared to offer price: won offers are cheaper
train %>% ggplot(aes(y=OFFER_PRICE, x=OFFER_STATUS, fill = OFFER_STATUS)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```

```{r}
# Won offers and total costs: won offers have lower costs
train %>% ggplot(aes(y=SERVICE_COST + MATERIAL_COST, x=OFFER_STATUS, fill = OFFER_STATUS)) +
  geom_boxplot() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))
```


```{r}
# Country by OFFER_STATUS
ggplot(train, aes(fill=OFFER_STATUS, x=COUNTRY.x)) + geom_bar(position="stack")
```

```{r}
## Offer status country
ggplot(train, aes(fill=OFFER_STATUS, x=TECH)) + geom_bar(position="stack")
```

```{r}
## Offer status to sales location
ggplot(train, aes(fill=OFFER_STATUS, x=SALES_BRANCH)) + geom_bar(position="stack")
```

## 3.2) Correlation Analysis

Correlation between numerical variables
```{r}
# Copy training dataset
numeric_train_df <- train

# Change OFFER_STATUS to numeric: WON = 1, LOST = 2
numeric_train_df <- numeric_train_df %>% mutate(
  OFFER_STATUS=as.numeric(OFFER_STATUS)
)

nums <- unlist(lapply(numeric_train_df, is.numeric))  
nums <- numeric_train_df[ , nums]  
correlations <- cor(nums)
corrplot(correlations)
```

Correlation of categorical variables. Small p-values (< 0.05) indicate a correlation between the dependent variable OFFER_STATUS and the categorical variables
```{r}
chisq.test(train$OFFER_STATUS, train$COUNTRY.x, correct=FALSE)
chisq.test(train$OFFER_STATUS, train$TECH, correct=FALSE)
chisq.test(train$OFFER_STATUS, train$SALES_BRANCH)
chisq.test(train$OFFER_STATUS, train$CURRENCY)
chisq.test(train$OFFER_STATUS, train$CURRENCY)
```

# 4) Training

## 4.1) Balance data

```{r}
print(nrow(train[train$OFFER_STATUS == "LOST",]))
print(nrow(train[train$OFFER_STATUS == "WON",]))

# sort train dataset
sorted <- train[order(train$OFFER_STATUS),]

# take first 7198 samples (3599 * 2)
sorted <- sorted[1:7198,]
shuffled <- sorted[sample(1:nrow(sorted)), ]

# create balanced train and validation datasets
balanced_train <- shuffled[1:5000,]
balanced_val <- shuffled[5001:6000,]

# check OFFER_STATUS distribution
print("TRAIN")
print(nrow(balanced_train[balanced_train$OFFER_STATUS == "LOST",]))
print(nrow(balanced_train[balanced_train$OFFER_STATUS == "WON",]))
print("VALIDATION")
print(nrow(balanced_val[balanced_val$OFFER_STATUS == "LOST",]))
print(nrow(balanced_val[balanced_val$OFFER_STATUS == "WON",]))
```

## 4.2) Train model

```{r}
# Create the forest.
model <- randomForest(OFFER_STATUS ~ . - CUSTOMER_ID,
                              data = balanced_train)
#model <- randomForest(OFFER_STATUS ~ SERVICE_COST + REV_CURRENT_YEAR.1 + SALES_BRANCH + BUSINESS_TYPE + OFFER_TYPE + REV_CURRENT_YEAR.2,
#                              data = balanced_train)


# View the forest results.
print(model)
# Importance of each predictor.
print(importance(model, type = 2))
```


Plot variables importance
```{r}
varImpPlot(model)
```

## 4.3) Evaluate Model

```{r}
balanced_val_preditions <- predict(model, newdata = balanced_val)
lvs <- c("LOST", "WON")
truth <- factor(balanced_val$OFFER_STATUS,
                levels = rev(lvs))
pred <- factor(
               balanced_val_preditions,               
               levels = rev(lvs))
xtab <- table(pred, truth)
confusionMatrix(xtab)
```

## 4.4.1) 

library(h2o)

h2o.init()
independent <- c(names(train))
independent <- independent[! independent %in% c("OFFER_STATUS")]

train <-  as.h2o(train)

h2o_auto = h2o.automl(y = "OFFER_STATUS", x = independent ,training_frame  = train, max_runtime_secs = 15000, seed = 2022) #currently set to ~4h
h2o_auto

## 4.4) Create submission

Predict OFFER_STATUS of the submission data

```{r}
submission_preditions <- predict(model, newdata = submission)
```

Create submission file

```{r}
submission_final <- submission
submission_final$OFFER_STATUS <- submission_preditions

print(nrow(submission_final[submission_final$OFFER_STATUS == "LOST",]))
print(nrow(submission_final[submission_final$OFFER_STATUS == "WON",]))

submission_file_df <- submission_final %>% select(TEST_SET_ID, OFFER_STATUS)
submission_file_df$OFFER_STATUS <- ifelse(submission_file_df$OFFER_STATUS == 'WON', 1, 0)
summary(submission_file_df)

write.csv(submission_file_df, 'predictions_fierce_pigeon_SUBMISSION_NUMBER.csv', row.names = FALSE)
```

```{r}
knitr::purl("index.Rmd")
```







